---
title: "EDA"
format: html
editor: visual
---

# Exploratory Data Analysis

This document includes all work necessary to perform Exploratory Data Analysis (EDA). EDA will help understand the data in general, including its basic features, distribution, etc..

## Library

List of libraries utilised in this document

```{r libraries}
library(tidyverse)
library(tidymodels)
library(here)
library(corrplot)
library(GGally)
library(readr)
```

## Data Exploration

### Data Loading

```{r data_loading}
kiwo <- read_csv(here("data/kiwo.csv"), col_names = TRUE)
train <- read_csv(here("data/train.csv"), col_names = TRUE)
test <- read_csv(here("data/test.csv"), col_names = TRUE)
wetter <- read_csv(here("data/wetter.csv"), col_names = TRUE)
```

### Data Understanding

#### Kiwo Dataset

-   Summary, Row Counts and Missing Value

```{r}
summary(kiwo)
nrow(kiwo)
sum(is.na(kiwo))
```

There is no missing value from `kiwo` dataset.

#### Train Dataset

-   Summary, Row Counts and Missing Value

```{r train_summ}
summary(train)
nrow(train)
sum(is.na(train))
```

There is no missing value from `train` dataset. Dates are in character type. Max Umsatz seems to be ridiculously high as compared to mean and 3rd quartile.

```{r}
train$Datum <- as.Date(train$Datum)
test$Datum <- as.Date(test$Datum)
wetter$Datum <- as.Date(wetter$Datum)
kiwo$Datum <- as.Date(kiwo$Datum)
```

```{r}
sum(duplicated(train$id))
```

No duplicates found in training set

-   Data Distribution

```{r train_dist}
hist(train$Warengruppe)
hist(train$Umsatz, breaks = 100)
```

It seems Warengrupe (category) 6 is the least frequent, appear below 500 times. On the other hand, other category seems appear about same amount of times. The sales dsitribution follows right-skewed distribution, where most of sales are recorded below 500.

```{r}
train |>
  select(Warengruppe) |>
  group_by(Warengruppe) |>
  summarise(n = n())
```

```{r}
ggplot(train, aes(x = as.factor(Warengruppe), y = Umsatz)) +
  geom_boxplot() +
  labs(title = "Sales By Product Category", x = "Warengruppe", y = "Umsatz")
```

A lot of outliers noticed and especially very high extreme values in 5 aka Cake sales. On average or median, product 2 and 5 aka rolls and cake have better sales as compared to 4 and 6 aka confectionery and seasonal bread.

#### Test Dataset

-   Summary, Row Counts and Missing Value

```{r test_summ}
summary(test)
nrow(test)
sum(is.na(test))
```

There is no missing value from `test` dataset.

-   Data Distribution

```{r test_dist}
hist(test$Warengruppe)
```

Similar to train dataset, here Warengrupper 6 is the least category to appear in the dataset.

#### Wetter Dataset

-   Summary, Row Counts and Missing Value

```{r wetter_summ}
summary(wetter)
nrow(wetter)
sum(is.na(wetter))
```

There are 679 missing value from `wetter` dataset.

-   Data Distribution

```{r wetter_dist}
hist(wetter$Bewoelkung)
hist(wetter$Temperatur)
hist(wetter$Windgeschwindigkeit)
hist(wetter$Wettercode)
```

### Data Merging

Several datasets will be combine with `Datum` as the primary key, and `train` as the base table. These datasets are `kiwo`, `train`, and `wetter`.

```{r merge}
train_data <- train |>
  left_join(kiwo, by = "Datum") |>
  left_join(wetter, by = "Datum") |>
  mutate(KielerWoche = ifelse(is.na(KielerWoche), 0, KielerWoche)) 
```

```{r train_data}
glimpse(train_data)
summary(train_data)
```

### Data Visualisations

#### Sales Trends

```{r}
train_data |>
  ggplot(aes(x = Datum, y = Umsatz)) +
  geom_point()
```

From the sales figures, it seems like there are 6 sales points that are unusual due to recording amounts above 1000. Some seasonality can be seen where during mid-year, sales are higher than the rest.

```{r}
ggplot(train, aes(x = Datum, y = Umsatz, color = as.factor(Warengruppe))) +
  geom_line() +
  labs(title = "Sales by Product Category", x = "Date", y = "Sales") +
  facet_wrap(~Warengruppe)
```

Looking at time series results, it looks like towards the end of the year, cake\[2\] has quite high sales. Most products seem to follow a sinusoidal pattern peaking sales at the center half of the calendar year(except cake\[2\]). Seasonal bread\[6\] only seems to make sales during the end months of the year, hence suggesting the name, seasonal bread.

-   Umsatz based on Warengruppe

```{r}
train_data |>
  ggplot(aes(x = as.factor(Warengruppe), y = Umsatz)) +
  geom_boxplot()
```

```{r summary}
# Umsatz (sales) by category
train_data %>%
  group_by(Warengruppe) %>%
  summarise(mean_umsatz = mean(Umsatz),
            sd_umsatz = sd(Umsatz),
            min_umsatz = min(Umsatz),
            max_umsatz = max(Umsatz))

# Plot sales by category
ggplot(train_data, aes(x = Datum, y = Umsatz, color = factor(Warengruppe))) +
  geom_line(alpha = 0.6) +
  facet_wrap(~ Warengruppe, scales = "free_y") +
  labs(title = "Sales over Time by Product Category", color = "Category")

```

Rolls and Cake have the highest average sales, but also high variability (std dev).

Seasonal Bread has the lowest average sales, likely due to being sold only during certain times.

Cake has the highest maximum sale value --- possibly due to occasional spikes in demand (e.g. holidays or events).

The plot shows that there is definitely seasonality in sales every year and some products have similar trends while some differ. Time series decomposition is necessary to understand the sales deeply.

#### Sales Relationship

-   Kieler Woche Event vs Regular Days Observations

```{r}
train_data |>
  ggplot(aes(x = as.factor(KielerWoche), y = Umsatz)) +
  geom_boxplot()
```

From the plot above, it does not seem Kieler Woche event differentiate the number of sales amount. This is evident from the median sales between them that are very close, and so does the box in overall.

-   Weather Observations

```{r}
# Bewoelkung vs Umsatz
train_data |>
  ggplot(aes(x = as.factor(Bewoelkung), y = Umsatz)) +
  geom_boxplot()

# Temperatur vs Umsatz
train_data |>
  ggplot(aes(x = Temperatur, y = Umsatz)) +
  geom_point()

# Windgeschwindigkeit vs Umsatz
train_data |>
  ggplot(aes(x = as.factor(Windgeschwindigkeit), y = Umsatz)) +
  geom_boxplot()

# Wettercode vs Umsatz
train_data |>
  ggplot(aes(x = as.factor(Wettercode), y = Umsatz)) +
  geom_boxplot()
```

Points taken: - It seems that Umsatz does not affected by Bewoelkung, as the numbers are pretty similar accross category. - Temperature wise, it does not seem matter to the Umsatz, supported by the fact that even in the extreme condition, there are still some high amount of Umsatz. - Windgeschwindigkeit or wind speed does not seem matter to Umsatz either, as the boxplots shows that they are positioned within the same range, and also having similar median values. - Again, the same case also exist for Wettercode, where it does not influence Umsatz.

In overall, it seems like weather does not play its part in influencing Umsatz, no matter how different the weather, Umsatz always have high and low amounts.

# Correlation between weather and sales

```{r}

ggplot(train_data, aes(x = Temperatur, y = Umsatz)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm") +
  facet_wrap(~ Warengruppe) +
  labs(title = "Sales vs Temperature by Category")
```

Bread and Confectionery are mostly temperature-insensitive, showing little to no change with fluctuating temperatures.

Rolls and Croissants demonstrate an increase in sales with temperature, suggesting that they are more likely to be purchased during warmer weather.

Cake shows a small positive trend, with slightly higher sales in warmer conditions, likely driven by seasonal factors or consumer behavior in certain temperature ranges.

Seasonal bread is mainly affected by colder temperatures, with a decrease in sales as temperatures rise, highlighting its seasonality.

```{r}
# Compare sales during vs outside Kieler Woche
train_data %>%
  group_by(KielerWoche, Warengruppe) %>%
  summarise(mean_umsatz = mean(Umsatz),
            sd_umsatz = sd(Umsatz)) %>%
  pivot_wider(names_from = KielerWoche, values_from = mean_umsatz, names_prefix = "sale_")

# Visualize
ggplot(train_data, aes(x = Datum, y = Umsatz, color = KielerWoche)) +
  geom_line(alpha = 0.4) +
  facet_wrap(~ Warengruppe) +
  labs(title = "Effect of Kieler Woche on Sales")

```

Sales for all categories appear to increase during Kieler Woche (e.g., Rolls go from \~399 → \~539).

Rolls and Croissant show large spikes in sales during KiWo.

This confirms that Kieler Woche significantly impacts sales, especially for high-demand or on-the-go items like Rolls and Croissants.

Some categories (like Confectionery) may show less of an increase, or even a slight decrease.

-   Correlation Matrix

```{r}
train_data |>
  select(Warengruppe, Umsatz, KielerWoche, Bewoelkung, Temperatur, Windgeschwindigkeit, Wettercode) |>
  cor(method = "pearson", use = "complete.obs") |>
  corrplot(method = 'number')
```

From the corrplot above, there is no variables that has high correlation, supported by the fact that the highest correlation is only 0.53.

#### Filtering Umsatz above 1000

```{r}
filtered_train_data <- train_data[train_data$Umsatz <= 1000, ]

glimpse(filtered_train_data)
```

-   Umsatz Trends

```{r}
filtered_train_data |>
  ggplot(aes(x = Datum, y = Umsatz)) +
  geom_point()
```

-   Umsatz based on Warengruppe

```{r}
filtered_train_data |>
  ggplot(aes(x = as.factor(Warengruppe), y = Umsatz)) +
  geom_boxplot()
```

Based on the figure above, Warengruppe 2 is the most sold group, followed by 5, 3, 1, 4, 6.

-   Weather Observations

```{r}
# Bewoelkung vs Umsatz
filtered_train_data |>
  ggplot(aes(x = as.factor(Bewoelkung), y = Umsatz)) +
  geom_boxplot()

# Temperatur vs Umsatz
filtered_train_data |>
  ggplot(aes(x = Temperatur, y = Umsatz)) +
  geom_point() +
  geom_smooth()

# Windgeschwindigkeit vs Umsatz
filtered_train_data |>
  ggplot(aes(x = Windgeschwindigkeit, y = Umsatz)) +
  geom_point() +
  geom_smooth()

# Wettercode vs Umsatz
filtered_train_data |>
  ggplot(aes(x = as.factor(Wettercode), y = Umsatz)) +
  geom_boxplot()
```

- Saving final dataset

```{r}
write_csv(filtered_train_data, "data/clean_data.csv")
```

